---
title: "Data Preprocessing"
author: "Jakub Raszka"
date: "22 7 2024"
output: word_document
---
## Packages & Functiions
```{r setup, include=FALSE}
#### Packages ####

# set wd
setwd("~/Documents/mindfulness-app")

# instal packages for loading
install.packages(pacman)
library(pacman)

# loading packages
p_load(
  tidyverse,
  ggplot2,
  psych,
  hms,
  data.table,
  lubridate,
  DescTools,
  fitdistrplus,
  lme4,
  pubh,
  tictoc,
  purrr,
  knitr
)

#### functions ####

## !intersect
outersect <- function(x, y, ...) {
  big.vec <- c(x, y, ...)
  duplicates <- big.vec[duplicated(big.vec)]
  setdiff(big.vec, unique(duplicates))
}

##  %!in%
"%!in%"  <- Negate("%in%")

## making a fuction which replaces content variable in specific courseId
content_modifier <- function(course_id, original, desired, dataM){

  dataM$content <- with(dataM,
     ifelse(content == original,
            ifelse(courseId == course_id, desired, dataM$content), dataM$content)
     )
  return(dataM)
}
```

## Loading data
```{r}
#### Data of 19 classes ####
data_path <- "raw_data/Data_thesis/"
files <- dir(data_path, pattern = "*.csv")

mindful_data <- files %>% 
  map(~ read_delim(file.path(data_path, .), delim = "\t", show_col_types = FALSE)) %>% 
  reduce(rbind)

#### Data of durations of recordings, week number and teacher id ####
 
# content type/type of practice
record_data <- read_delim("raw_data_modified/Copy of Student_descriptions_2509.csv", delim = ";", show_col_types = FALSE)
record_data[,c("X4", "X5", "record_duration")] <- NULL

# prescribed duration of recordings
record_data_dur <- read.delim("raw_data_modified/Record_duration_good_format.txt", header = F)
colnames(record_data_dur) <- "duration"

# teacher id
teacher_id_data <- read_delim("raw_data_modified/Teacher_id_course_id.csv", delim = ";", show_col_types = FALSE)
teacher_id_data[c("X3", "X4", "X5")] <- NULL

# week number
week_n <- read_delim("raw_data_modified/Correct_week_number.csv", delim = ";", show_col_types = FALSE)

#### Manual adjustments ####
## adding zero at the begining of two id course
week_n$courseId <- ifelse(week_n$courseId == 21626, sprintf("%06d", 021626), week_n$courseId)
week_n$courseId <- ifelse(week_n$courseId == 66437, sprintf("%06d", 066437), week_n$courseId)


## renaming column to match other data frames
names(week_n)[names(week_n) == "cor_week_number"] <- "week_number_c"

#### Demo data ####
# loading demo data
data_path_demo <- "raw_data/Demographics_students/"
files_demo <- dir(data_path_demo, pattern = "*.csv")

data_demo <- files_demo %>% 
  map(~ read_delim(file.path(data_path_demo, .), delim = "\t", show_col_types = FALSE)) %>% 
  reduce(rbind)

```

## Merge data
```{r}
# merging content, prescribed duration of practice
record_data <- cbind(record_data, record_data_dur)

#changing duration to a date class
record_data$duration <- ms(record_data$duration)


## splitting multiple course values per content
record_data <- separate_rows(record_data,courseId,sep="[[:space:]]")

# merging teacher id and content, duration
record_data <- merge(teacher_id_data, record_data)

## excluding courseId of CCT and one tutorial (diabetis), not supposed to be part of analysis!
record_data <- dplyr::filter(record_data, courseId != 643761 & courseId != 545252
 & courseId != 864491)

## keep only desired columns # has to do that also for super_df_timer later on
#record_data <- record_data %>% select(c("courseId", "teacherId", "Content", "duration"))
```



## Various formats of data
```{r}
##using lubridate package to change the format of the start and end time
mindful_data$startTime <- ymd_hms(mindful_data$startTime)
mindful_data$endTime <- ymd_hms(mindful_data$endTime)

# extracting a weekday name i
## since I am on non-english computer
Sys.setlocale("LC_TIME", "C")

mindful_data$weekday <- lubridate::wday(mindful_data$startTime, label = TRUE, abbr = FALSE)# locale = Sys.setlocale(category = "LC_ALL", locale = "English"))


# calculating the inaccurate duration from start and end of session
mindful_data$duration_start_end <- mindful_data$endTime - mindful_data$startTime


# extracting weekday and weekend
mindful_data$day_type <- ifelse(mindful_data$weekday == "Saturday" | mindful_data$weekday == "Sunday", "weekend", "weekday")
```


Multiple problems with value consistency found, namely in column courseId and content. In courseId, one value had space at the begining, two others missed zero at the begining.
We found more inconsistencies in the content. Several spaces at the end of variable (only in mindful_data), capital letters at words' begining used interchangeably and the list goes on...



## Format inconsistencies
```{r}
#### mindful dataset ####

## lowercase content
mindful_data$content <- tolower(mindful_data$content)

## removing space at the end or beginning
mindful_data$content <- trimws(mindful_data$content)

## "Body Scan" -> "Bodyscan"
mindful_data$content <- ifelse(mindful_data$content == "body scan", "bodyscan", mindful_data$content)

## two version of Kor meditation
mindful_data$content[grepl("kort meditation", mindful_data$content)] <- "kort meditation andedraet og krop"

## eliminating danish special punctuation
mindful_data$content[grepl("k og siddende meditation", mindful_data$content)] <- "staende straek og siddende meditation"

## renaming correctly named sesion for course Id 710798
mindful_data <- content_modifier(710798, "liggende yoga", "lang liggende yoga", mindful_data)


#### record data  ####

## renaming content name for the sake of consistency

if("Content" %in% colnames(record_data)){
  
 record_data <- record_data %>% 
   dplyr::rename("content" = "Content") 
}


## lowercase content
record_data$content <- tolower(record_data$content)

## removing space at the end or beginning
record_data$content <- trimws(record_data$content)


## two versions of Kort meditation
record_data$content[grepl("kort meditation", record_data$content)] <- "kort meditation andedraet og krop"

## unify different versions of body scan
record_data$content <- ifelse(record_data$content == "body scan", "bodyscan", record_data$content)

## eliminating danish special punctuation
record_data$content[grepl("k og siddende meditation", record_data$content)] <- "staende straek og siddende meditation"



##  adding missing zero at the begining of two courseId
record_data$courseId <- ifelse(record_data$courseId == 21626, sprintf("%06d", 021626), record_data$courseId)

record_data$courseId <- ifelse(record_data$courseId == 66437, sprintf("%06d", 066437), record_data$courseId)

## 710798 missing one combination of course id and content in record_data -> adding it manually
record_data <- record_data %>% 
  add_row(courseId = "710798", teacherId = 1, content = "staende straek og siddende meditation", duration = ms("49:28"))


#### unyfying practise type into 3 categories  ####

mindful_data <- mindful_data %>%
  dplyr::mutate(practice_type = case_when(
    grepl("scan", content) ~ "bodyscan",
    grepl("yoga", content) ~ "yoga",
    grepl("musik|loving kindness.|og.krop|meditation", content) ~ "meditation"
  ))

```

## CourseId stats

```{r}
# number of classes, sd, mean
mindful_data %>% group_by(courseId) %>% dplyr::summarise(n = n_distinct(studentId)) %>% describe(.)
```


## Calculating duration from start time and progress, merging

```{r}
#### Merge ####
# merging dataframe
super_df <- merge(record_data, mindful_data, by = c("content", "courseId"), all.y = T)


# getting duration for timer (from start_time_duration)

## calculating duration based on progress and recording duration
super_df$duration <- as.numeric(super_df$duration)
super_df$recording_duration <- super_df$duration


## calculation
super_df$duration <- super_df$progress/100*super_df$recording_duration
super_df$duration <- round(super_df$duration, digits = 0)



#### aligning duration formats ####

super_df$duration_start_end <- super_df$endTime - super_df$startTime
super_df$duration_start_end <- as.numeric(super_df$duration_start_end)


## replacing NA in content with timer
super_df$content[is.na(super_df$content)]  <- "timer"


## replacing NA values

super_df$duration <- ifelse(is.na(super_df$duration), super_df$duration_start_end, super_df$duration)
super_df$content[is.na(super_df$content)]  <- "timer"  
super_df$practice_type[is.na(super_df$practice_type)]  <- "timer"  
super_df$teacherId[is.na(super_df$teacherId)]  <- 0  
super_df$recording_duration[is.na(super_df$recording_duration)]  <- 0 

## extracting unique number for a day
super_df$ymd_numeric <- as.numeric(date(super_df$startTime))


## creating a teach id with correct courseIds
teacher_id_data_timer <- teacher_id_data

teacher_id_data_timer$courseId <- 
  ifelse(teacher_id_data_timer$courseId == 21626, sprintf("%06d", 021626), teacher_id_data_timer$courseId)
teacher_id_data_timer$courseId <- 
  ifelse(teacher_id_data_timer$courseId == 66437, sprintf("%06d", 066437), teacher_id_data_timer$courseId)


## getting full info for "timer" data as well (not working because of no info for content column)
super_df_timer <- super_df %>% dplyr::filter(type == "timer") %>% 
  dplyr::select(-c("teacherId")) %>% 
  merge(teacher_id_data_timer)

## deleting "merging" columns with no sense
#super_df_time <- super_df_timer[,1:16]

## merging complete timer and no-timer data
super_df <- super_df %>% filter(type != "timer") %>% 
  add_row(super_df_timer)

#### exclusion CHART-FLOW ####
nrow(super_df)
n_distinct(super_df$studentId)
```


## Data exclusion
```{r}
# deleting progress >100  & duration <119 and duration > 4000

super_df <- filter(super_df, progress <=100 & duration >= 119 & duration < 4000)

# deleting randomly created NA columns with no fuction
super_df <- select(super_df, -contains("."))

# deleting NA values
## viewing what is to be deleted
super_df %>% filter_all(any_vars(is.na(.))) 

## deleting
super_df <- na.omit(super_df)

#### exclusion CHART-FLOW ####
nrow(super_df)
n_distinct(super_df$studentId)
## excluded
18877 - nrow(super_df)

# participant calculation
346 - n_distinct(super_df$studentId)

# exlusion of "too long" sessions - 14 in total, some of them wouldn`t make it through next cleaning steps anyway
```


## Subsequences loop

Assumptions that the loop makes:
- progress is not corrupt and was functioning during the entire mindfulness program
- overlapping sessions: if the progress is growing during the same day, it is the same session/observation split into multiple sessions/observations (due to an interruption, for instance) and therefore only the one with the highest progress within one subsequence (sessions with growing progress) counts 
- people were honestly and fully engaging with their practices during the entire recording duration 

```{r}
#### List to iterate over with the loop ####
# Get all student and day combinations with more than 1 session
super_df_comb <- super_df %>%
  group_by(studentId, ymd_numeric) %>%
  dplyr::summarise(freq = n()) %>%
  dplyr::filter(freq > 1)

# Precise number of sessions from the days with more than 1 session 
sum(super_df_comb$freq)

# List to store the cleaned data (after running the loop)
indices <- list()

# Results list iterator
list_iter <- 1

#### Loop ####
# Loop for dealing with overlapping sessions and the build-up issue with progress

## loop for finding subsequences and keeping only one session with the highest progress per subsequence

for (i in seq(nrow(super_df_comb))) {
  one_combination <- super_df_comb[i, ] 
  
  # filter all sessions per one day per participant and arrange it by the start time and progress
  df_day <- super_df %>%
    filter(
      studentId == one_combination$studentId,
      ymd_numeric == one_combination$ymd_numeric) %>%
    arrange(startTime, progress)

  # finding indices of sessions´ subsequences per student per day
  # example: https://stackoverflow.com/questions/55515798/find-all-subsequences-with-specific-length-in-sequence-of-numbers-in-r
  indices_loop <- sapply(split(1:length(df_day$progress),
                                cumsum(c(
                                  0, (diff(df_day$progress)
                                ) + 1) < 1)), # change from <1 to <=1?
                          function(x)
                            if (length(df_day$progress) >= 2)
                              c(start = x[1], end = x[length(x)]))
  
 
  indices_loop <- as.data.frame(t(indices_loop))
  
  # for every group of subsequences filter only the session with the highest progress
  for (i in 1:nrow(indices_loop)) {
    start <- indices_loop[i, 1]
    end <-  indices_loop[i, 2]
    
    df <- df_day[start:end, ]
    df <- df %>% arrange(desc(progress)) %>% head(1)
    
    # appending the cleaned subsequences to the list
    indices[[list_iter]] <- df
    list_iter <- list_iter + 1 
    
  }
}

# unlisting the cleaned subsequences list
indices_df <- do.call("rbind", indices)

#indices_df <- NULL
## adding the observations with 1 session per day per student to the cleaned subsequences dataframe (multiple sessions per student per day)
clean_df <- super_df %>%
  group_by(studentId, ymd_numeric) %>%
  dplyr::mutate(n_session_per_day = n()) %>%
  dplyr::filter(n_session_per_day == 1) %>%
  full_join(indices_df)

clean_df %>%
  group_by(studentId, ymd_numeric) %>%
  dplyr::mutate(n_session_per_day = n()) %>%
  #dplyr::filter(n_session_per_day == 2) %>%
  group_by(studentId) %>%
  dplyr::summarise(n_session = n()) 

#### Loop check ####
# Examples with separate students to confirm that the cleaning worked

super_df %>%
  filter(studentId == "181087" & ymd_numeric == 18338) %>%
  arrange(startTime)

clean_df %>%
  filter(studentId == "015365" & ymd_numeric == 18299) %>% 
  arrange(startTime)


super_df %>%
  filter(studentId == "245558" & ymd_numeric == 18391) %>% 
  arrange(startTime)

clean_df %>%
  filter(studentId == "245558" & ymd_numeric == 18391) %>% 
  arrange(startTime)


#### exclusion CHART-FLOW ####
nrow(clean_df)
n_distinct(clean_df$studentId)
15037-10730

```



## Creating variables

#### Day period
```{r}
fulldata_clean <- clean_df

# changing format
fulldata_clean$hms_startTime <- as.numeric(as_hms(fulldata_clean$startTime))

# empty vector
fulldata_clean$day_period <- c("l")

## making the day period
for(i in 1:nrow(fulldata_clean)){
  
  if(fulldata_clean$hms_startTime[i] < 18000){
    fulldata_clean$day_period[i] <- "night"
    
    } else if(fulldata_clean$hms_startTime[i] >= 18000 & fulldata_clean$hms_startTime[i] < 43200){
     fulldata_clean$day_period[i] <- "morning"  
    
    } else if(fulldata_clean$hms_startTime[i] >= 43200 & fulldata_clean$hms_startTime[i] < 61200){
     fulldata_clean$day_period[i] <- "afternoon"  
     
    } else(fulldata_clean$day_period[i] <- "evening")
  }


```


### Exclusion beyond MBSR
```{r}
#### Reload data ####
# loading week number data (the reason for doing it here is that when we re-run the code, the date format of some columns changes, so we need to re-load the data to keep it in the original form whenever re-running the code)

# week number
week_n <- read_delim("raw_data_modified/Correct_week_number.csv", delim = ";")

## adding zero at the begining of two id course
week_n$courseId <- ifelse(week_n$courseId == 21626, sprintf("%06d", 021626), week_n$courseId)
week_n$courseId <- ifelse(week_n$courseId == 66437, sprintf("%06d", 066437), week_n$courseId)

## renaming column to match other data frames
names(week_n)[names(week_n) == "cor_week_number"] <- "week_number_c"

#### Loop ####
### making end time column for looping

## changing into right format
week_n$week_start <- as.Date(dmy(week_n$week_start))



# empty column for loop output
week_n$week_end <- as.Date("")

for(i in 1:nrow(week_n)){
  if(week_n$week_number_c[i] <= 7){
   week_n$week_end[i] <- week_n$week_start[i+1] - 1 
  
   } else(week_n$week_end[i] <- week_n$week_start[i] + 6)
  
}

# changing classes
week_n$week_start <- as.Date(week_n$week_start)
week_n$week_end <- as.Date(week_n$week_end)

##### creating a sequence of all day between start and end time so we can merge it with session data

# empty dataframe for the loop's output
empty_df <- data.frame()

#### Lopp for sequences ####
##  creating sequence of week start and week end
for(i in 1:nrow(week_n)){
  day = seq.Date(week_n$week_start[i], week_n$week_end[i], by = 1)
  
  all = cbind(day, week_n$courseId[i], week_n$week_number_c[i])
  empty_df <- rbind(empty_df, all)
}

# changing into the right format
empty_df$day <- as.Date(as.numeric(empty_df$day), origin = "1970-01-01")


## changing names         
names(empty_df)[names(empty_df) == "V2"] <- "courseId"
names(empty_df)[names(empty_df) == "V3"] <- "week_number_c"

## adding a date variable for merging dataframes
fulldata_clean$day <- as.Date(fulldata_clean$startTime)


## merging -> deletion of sessions practiced beyond program!
fulldata_clean <- merge(fulldata_clean, empty_df, by = c("courseId", "day"))


fulldata_clean <- merge(fulldata_clean, week_n, by = c("courseId", "week_number_c"))


#### exclusion CHART-FLOW ####
nrow(fulldata_clean)
n_distinct(fulldata_clean$studentId)
10730-7996



## save empty_df with start time and end 
program_week_starend <- empty_df %>% group_by(courseId, week_number_c) %>% 
  dplyr::summarise(program_week_start = min(day),
                   program_week_end = max(day))

#write_csv(program_week_starend, "created_data/program_week_start_end.csv")

```




#### Calendar week number
```{r}

# creating correct week start from the week start
df7_horse <- fulldata_clean

df7_horse$w_number_accurate <- NA
df7_horse$week_start_accurate <- NA
df7_horse$week_end_accurate <- NA

df7_horse$day <- as.Date(df7_horse$day)
df7_horse$week_start <- as.Date(df7_horse$week_start)

list7_mink <- list()

  
for (i in levels(as.factor(df7_horse$studentId))){
  W1 <- df7_horse[df7_horse$studentId == i,]
  #print(unique(W1$studentId))
  
  program_start <- min(W1$week_start)
  #print(program_start)
  
  
  for (w in 1:nrow(W1)){
    
      ## W1
    if(W1$day[w] %within% interval(program_start, (program_start + 6))){
      
      W1$w_number_accurate[w] <- 1
      W1$week_start_accurate[w] <- program_start
      W1$week_end_accurate[w] <- program_start + 6
    
      ## W2
    } else if(W1$day[w] %within% interval((program_start + 7), (program_start + 13))){
      
      W1$w_number_accurate[w] <- 2
      W1$week_start_accurate[w] <- program_start + 7
      W1$week_end_accurate[w] <- program_start + 13  
    
      ## W3    
    } else if(W1$day[w] %within% interval((program_start + 14), (program_start + 20))){
      
      W1$w_number_accurate[w] <- 3
      W1$week_start_accurate[w] <- program_start + 14
      W1$week_end_accurate[w] <- program_start + 20  
    
      ##  W4  
    } else if(W1$day[w] %within% interval((program_start + 21), (program_start + 27))){
      
      W1$w_number_accurate[w] <- 4
      W1$week_start_accurate[w] <- program_start + 21
      W1$week_end_accurate[w] <- program_start + 27
    
      ## W5    
    } else if(W1$day[w] %within% interval((program_start + 28), (program_start + 34))){
      
      W1$w_number_accurate[w] <- 5
      W1$week_start_accurate[w] <- program_start + 28
      W1$week_end_accurate[w] <- program_start + 34 
    
      ## W6    
    } else if(W1$day[w] %within% interval((program_start + 35), (program_start + 41))){
      
      W1$w_number_accurate[w] <- 6
      W1$week_start_accurate[w] <- program_start + 35
      W1$week_end_accurate[w] <- program_start + 41 
   
       ## W7    
    } else if(W1$day[w] %within% interval((program_start + 42), (program_start + 48))){
      
      W1$w_number_accurate[w] <- 7
      W1$week_start_accurate[w] <- program_start + 42
      W1$week_end_accurate[w] <- program_start + 48 
    
      ## W8    
    } else if(W1$day[w] %within% interval((program_start + 49), (program_start +  55))){
      
      W1$w_number_accurate[w] <- 8
      W1$week_start_accurate[w] <- program_start + 49
      W1$week_end_accurate[w] <- program_start + 55 
    
      ## W9    
    } else if(W1$day[w] %within% interval((program_start + 56), (program_start + 62))){
      
      W1$w_number_accurate[w] <- 9
      W1$week_start_accurate[w] <- program_start + 56
      W1$week_end_accurate[w] <- program_start + 62 
    
      ## W10   
    } else if(W1$day[w] %within% interval((program_start + 63), (program_start + 69))){
      
      W1$w_number_accurate[w] <- 10
      W1$week_start_accurate[w] <- program_start + 63
      W1$week_end_accurate[w] <- program_start + 69 
    
      ## W11    
    } else{
      W1$w_number_accurate[w] <- 11
      W1$week_start_accurate[w] <- program_start + 70
      W1$week_end_accurate[w] <- program_start + 76 
    }
  }
  list7_mink[[i]] <- W1
}

df7_mink <- do.call(rbind, list7_mink)

rownames(df7_mink) <- NULL


```


#### binary covid participant & session level
```{r}

covid_bin <- data.frame()

for(i in levels(as.factor(df7_mink$studentId))){
 P2 <- df7_mink[df7_mink$studentId == i,]
  
  if(
    min(P2$startTime) %within% interval(as.Date("2019-02-24"), as.Date("2020-02-29")) & 
    max(P2$startTime) %within% interval(as.Date("2020-03-23"), as.Date("2020-07-29"))){
  
    P2$covid_period <- "yes"
  
    } else(P2$covid_period <- "no")
 
 covid_bin <- rbind(covid_bin, P2)
}

## session level
covid_bin$covid_session <- c()

for(i in 1:nrow(covid_bin)){
  
  if(covid_bin$day[i] <= as.Date("2020-03-11")){
    covid_bin$covid_session[i] <- "no"
    
    } else(covid_bin$covid_session[i] <- "yes")
  }


## excluding 1 session of on eparticipant who did practice 2 weeks after the end of 7th week because of holiday
#covid_bin <- filter(covid_bin, week_number != 12)

```


## Check split sessions
```{r}
# duration >120 s & program weeek <=8
covid_bin %>% 
   filter(studentId == "245558" & ymd_numeric == 18352) %>% 
  arrange(startTime)

suspc_exam <- fulldata_clean %>%
  filter(studentId == "831532" & ymd_numeric == 18028) %>% 
  arrange(startTime)

super_df %>%
  filter(studentId == "831532" & ymd_numeric == 18028) %>% 
  arrange(startTime)

```


## Data exclusion ITT
```{r}
# exclusion based on ITT (intention-to-treat concept) -> at least 3 session beyond first week

## at least 1 session done in other week than 3rd
IIT_list <- list()

for (i in levels(as.factor(covid_bin$studentId))){
  G1 <- covid_bin[covid_bin$studentId == i,]
  
  G1$n_session <- length(G1$studentId)
  
  G1$IIT <- ifelse(G1$n_session >=3 & max(G1$w_number_accurate >=2), 1, 0)
  # if(G1$n_session >= 3 & max(G1$w_number_accurate) >= 2){
  #   G1$IIT <- 1
  #   
  # } else{G1$IIT <- 0}
  IIT_list[[i]] <- G1
}

IIT <- do.call("rbind", IIT_list)

# removing strange row names
rownames(IIT) <- NULL

IIT <- IIT %>% filter(IIT == 1) # 289 participants out of 320

length(unique(covid_bin$studentId))



IIT %>% filter(IIT == 0) %>% summarise(count = length(unique(studentId)))

working_df <- covid_bin %>% subset(studentId %in% IIT$studentId) 

IIT %>% 
  filter(IIT == 1) %>% 
  group_by(studentId) %>% 
  dplyr::summarise(sessionn = n()) %>% 
  mutate(average_n_s= mean(sessionn)) %>% 
  arrange(desc(sessionn))


# adding gender column for analysing favourite practice in week 7,8
working_df <- distinct(merge(working_df, data_demo[,c(2,4)], by = "studentId", all.x = T))


# exclusion CHART-FLOW
nrow(working_df)
n_distinct(working_df$studentId)

7996 - nrow(working_df)

# adding program week start and end
# merge(working_df, program_week_starend, by = c("week_number_c", "courseId")) no need to, it is already there

```

## Write data
```{r}
# sorting columns
working_df <- working_df %>%
  dplyr::mutate(program_week = week_number_c,
                calendar_week = w_number_accurate) 


# write down 8 PROGRAM WEEK DF
#write_csv(working_df, "created_data/df_8_program_weeks.csv")

# write down 6 PROGRAM WEEK DF
working_df6 <- filter(working_df, week_number_c <= 6)

#write_csv(working_df6, "created_data/df_6_program_weeks.csv")
```

